Paper_stuff

### 2024-01-24 Paper_stuff.Rmd
Restarting paper

# Import data

Read in the dataset. 
```{r}
Mothership <- read_sav("~/Desktop/Coding/data/PHPoutcome_clean.sav")
View(df)
```

@@

## Export as CSV
```{r}
write.csv(Mothership,"~/Desktop/Coding/data/Mothership_paper")
```

Disorder_varaibles
```{r}

@@

# df with and without depression
No_depressy <- Mothership_Diag %>%
  filter(Disorder_Type != "Mood")
```

Pre_Post
### Extract pre/post scores
```{r}
#1. load DF
    Mothership_post <- Mothership_Diag_treat

@@

    # Anxiety
    Pre_ANX <- NA
    PA_df <- NA
    for(i in 1:nrow(CUXOS_Score_pre)){
    PA_df <- unname(unlist(CUXOS_Score_pre[i,]))
    PA_df <- PA_df[!is.na(PA_df)]
    PA_df <- head(PA_df, n=1)
    Pre_ANX <- rbind(Pre_ANX,PA_df)
    }
    Pre_anx <- Pre_ANX[-1]

@@

              #deprssion values Symptom severity: 0-10 (remission), 11-20 (minimal), 21-30 (mild), 31-45 (moderate), 46+ (severe)"
        BL_Dep_level = as.factor(ifelse(BL_CUDOS > 10 & BL_CUDOS <= 20, "Minimal",
                                 ifelse(BL_CUDOS > 20 & BL_CUDOS <= 30, "Mild",
                                 ifelse(BL_CUDOS > 10 & BL_CUDOS <= 45, "Moderate",
                                 ifelse(BL_CUDOS > 45, "Severe",
                                 ifelse(is.na(BL_CUDOS), NA, "Remission"
                                )))))),
        BL_Anx_level = as.factor(ifelse(BL_CUXOS > 10 & BL_CUXOS <= 20, "Minimal",
                                 ifelse(BL_CUXOS > 20 & BL_CUXOS <= 30, "Mild",
                                 ifelse(BL_CUXOS > 10 & BL_CUXOS <= 45, "Moderate",
                                 ifelse(BL_CUXOS > 45, "Severe",
                                 ifelse(is.na(BL_CUXOS), NA, "Remission"
                                )))))),
        Post_Dep_level = as.factor(ifelse(CUDOS_post > 10 & CUDOS_post <= 20, "Minimal",
                                 ifelse(CUDOS_post > 20 & CUDOS_post <= 30, "Mild",
                                 ifelse(CUDOS_post > 10 & CUDOS_post <= 45, "Moderate",
                                 ifelse(CUDOS_post > 45, "Severe",
                                 ifelse(is.na(CUDOS_post), NA, "Remission"
                                )))))),
        Post_Anx_level = as.factor(ifelse(CUXOS_post > 10 & CUXOS_post <= 20, "Minimal",
                                 ifelse(CUXOS_post > 20 & CUXOS_post <= 30, "Mild",
                                 ifelse(CUXOS_post > 10 & CUXOS_post <= 45, "Moderate",
                                 ifelse(CUXOS_post > 45, "Severe",
                                 ifelse(is.na(CUXOS_post), NA, "Remission"
                                )))))))
    ```

Responders
```{r}
#devtools::install_github("AWKruijt/JT-RCI")

library(JTRCI)

#devtools::install_github("zieglema/ClinicalSig")
library(ClinicalSig)
# generate some random data:

@@

RCI_DF
```

RCI
    ```{r}
Mothership_post <- Mothership_post |>
  #1. Filter out scores for people not in the program / don't have dataa
  filter(!is.na(Days_complete_1)) |>
    #Having people in the program for more than 40 days means that their scores may be a lot higher, they should be filtered out as result. 
  filter(!is.na(CUXOS_pre),
         !is.na(CUXOS_post),
         CUXOS_pre > 0,
         CUXOS_post >= 0,
         !is.na(CUDOS_pre),
         !is.na(CUDOS_post),
         CUDOS_pre > 0,
         CUDOS_post> 0
         ) |>
  mutate(
    Delta_Anx_DC =  CUXOS_post - CUXOS_pre,
    Delta_Dep_DC = CUDOS_post - CUDOS_pre,
    Percent_Anx_change = (Delta_Anx_DC/CUXOS_pre)*100,
    Percent_Dep_Dchange = (Delta_Dep_DC/CUDOS_pre)*100,
    #Days_complete_W = ifelse(Days_complete_1 > 40, 40, Days_complete_1),
    Anx_Responder = as.factor(
      ifelse(CUXOS_pre < 20 & Percent_Anx_change  <= -50, "Responder",
      ifelse(CUXOS_pre < 20 & Percent_Anx_change  > -50,  "Unresponders", NA)   
      )),
    Dep_Responder = as.factor(
      ifelse(CUDOS_pre < 20 & Percent_Dep_Dchange <= -50, "Responder",
      ifelse(CUDOS_pre < 20 & Percent_Dep_Dchange > -50,   "Unresponders", NA) 
      )),
    Treatment_Responder = as.factor(
      ifelse(CUXOS_pre > 10 & CUXOS_pre > 10 & Percent_Anx_change  <= -50 & Percent_Anx_change < 0 & Percent_Dep_Dchange < 0 & Percent_Dep_Dchange <= -50, "Both_Responder", 
      ifelse(CUXOS_pre > 10 & Percent_Anx_change  <= -50, "Anx Responder",
      ifelse(CUDOS_pre > 10 & Percent_Dep_Dchange <= -50, "Dep Responder",
      ifelse(CUDOS_pre > 10 & Percent_Dep_Dchange > 0 & CUXOS_pre > 10 & Percent_Anx_change > 0, "Both Worse",
      ifelse(CUXOS_pre > 10 & Percent_Anx_change > 0, "Anx Worse",
      ifelse(CUDOS_pre > 10 & Percent_Dep_Dchange > 0, "Dep Worse",
      ifelse(CUXOS_pre > 10 & CUDOS_pre > 10 & Percent_Anx_change < 0 & Percent_Anx_change > -50 & Percent_Dep_Dchange < 0 & Percent_Dep_Dchange > -50, "Both Unresponder",
      ifelse(CUDOS_pre > 10 & Percent_Dep_Dchange < 0 & Percent_Dep_Dchange > -50, "Dep Unresponders", 
      ifelse(CUXOS_pre > 10 & Percent_Anx_change < 0 & Percent_Anx_change > -50, "Anx Unresponders", "Low Baseline"
      )))))))))))

Mothership_post <- left_join(Mothership_post,RCI_DF, by = join_by(ID1)) |>
  mutate(
    Depression_Responder = ifelse(!is.na(class_RCI_dep), class_RCI_dep, NA),
      Depression_Responder = as.factor(recode(Depression_Responder,
         "1" = "2",
         "2" = "2",
         "3" = "1"
      )),
    Depression_Responder = as.factor(ifelse(!is.na(Depression_Responder), Depression_Responder, Dep_Responder)),
         Depression_Responder = as.factor(recode(Depression_Responder,
          "2" = "Non-Responder",
          "1" = "Responder"
      )),
    Anxiety_Responder = ifelse(!is.na(class_RCI_anx), class_RCI_anx, NA),
      Anxiety_Responder = as.factor(recode(Anxiety_Responder,
         "1" = "2",
         "2" = "2",
         "3" = "1"
      )),
    Anxiety_Responder = as.factor(ifelse(!is.na(Anxiety_Responder), Anxiety_Responder, Anx_Responder)),
         Anxiety_Responder = as.factor(recode(Anxiety_Responder,
          "2" = "Non-Responder",
          "1" = "Responder"
      )),
    RESPONDER_FIGS = as.factor(
        ifelse(Anxiety_Responder == "Responder" | Depression_Responder == "Responder", "Responder",
        ifelse(Anxiety_Responder == "Non-Responder" & Depression_Responder == "Non-Responder", "Non-Responder", NA)
        )))

# View(Mothership_joined)
```

AnxDep_PrePost
    ```{r}
#7. create new DF with Varaibles we want

@@

### Dumbell Plot by Disorder
```{r}
Pre_ANX<-ANX_PrePost_mean %>%
  filter(PrePost == "Pre")

ggplot(data=Pre_ANX,
       aes(x=Disorder_Type,y=Score,
           group=Disorder_Type,color=Disorder_Type))+
  geom_segment(aes(x=Disorder_Type, xend=Post_ANX$Disorder_Type, y=Score, yend=Post_ANX$Score),color = "#ad3e4f",
              size = 4, #Note that I sized the segment to fit the points
              alpha = .5) +
  geom_point( aes(x=Disorder_Type, y=Score), color= "#F90000", size=3.5) +
  geom_point( aes(x=Post_ANX$Disorder_Type, y=Post_ANX$Score), color= "#0CC541", size=3.5) +
  labs(title = "Mean Pre and Post Anxiety Scores By Disorder Type",
       subtitle = "Self Report anxiety was assessed using the CUXOS",
       caption = "Symptom severity: 0-10 (remission), 11-20 (minimal), 21-30 (mild), 31-40 (moderate), 41+ (severe)")+
  scale_y_reverse(limits = c(45,15)) +
  coord_flip() +
  theme_classic()+
  theme(#legend.position = "none",
         plot.background = element_rect(
      fill = "white",
      colour = "white"))

ggplot(data=Pre_DEP,
       aes(x=Disorder_Type,y=Score,
           group=Disorder_Type,color=Disorder_Type))+
  geom_segment(aes(x=Disorder_Type, xend=Post_DEP$Disorder_Type, y=Score, yend=Post_DEP$Score),color = "#4068a8",
              size = 4, #Note that I sized the segment to fit the points
              alpha = .5) +
  geom_point( aes(x=Disorder_Type, y=Score), color= "#F90000", size=3.5) +
  geom_point( aes(x=Post_DEP$Disorder_Type, y=Post_DEP$Score), color= "#0CC541", size=3.5) +
  labs(title = "Mean Pre and Post Depression Scores By Disorder Type",
       subtitle = "Self Report anxiety was assessed using the CUDOS",
       caption = "Symptom severity: 0-10 (remission), 11-20 (minimal), 21-30 (mild), 31-45 (moderate), 46+ (severe)",
       ylab = "Disorder Type")+
  scale_y_reverse(limits = c(45,15)) +
  coord_flip() +
  theme_classic()+

  theme(#legend.position = "none",
         plot.background = element_rect(
      fill = "white",
      colour = "white"))
```

```{r}
Mothership_post <- Mothership_post |>
  #1. Filter out scores for people not in the program / don't have dataa
  filter(!is.na(Days_complete_1)) |>
    #Having people in the program for more than 40 days means that their scores may be a lot higher, they should be filtered out as result. 
  filter(!is.na(CUXOS_pre),
         !is.na(CUXOS_post),
         CUXOS_pre > 0,
         CUXOS_post >= 0,
         !is.na(CUDOS_pre),
         !is.na(CUDOS_post),
         CUDOS_pre > 0,
         CUDOS_post> 0
         ) |>
  mutate(
    Delta_Anx_DC =  CUXOS_post - CUXOS_pre,
    Delta_Dep_DC = CUDOS_post - CUDOS_pre,
    Percent_Anx_change = (Delta_Anx_DC/CUXOS_pre)*100,
    Percent_Dep_Dchange = (Delta_Dep_DC/CUDOS_pre)*100,
    #Days_complete_W = ifelse(Days_complete_1 > 40, 40, Days_complete_1),
    Anx_Responder = as.factor(
      ifelse(CUXOS_pre < 20 & Percent_Anx_change  <= -50, "Responder",
      ifelse(CUXOS_pre < 20 & Percent_Anx_change  > -50,  "Unresponders", NA)   
      )),
    Dep_Responder = as.factor(
      ifelse(CUDOS_pre < 20 & Percent_Dep_Dchange <= -50, "Responder",
      ifelse(CUDOS_pre < 20 & Percent_Dep_Dchange > -50,   "Unresponders", NA) 
      )),
    Treatment_Responder = as.factor(
      ifelse(CUXOS_pre > 10 & CUXOS_pre > 10 & Percent_Anx_change  <= -50 & Percent_Anx_change < 0 & Percent_Dep_Dchange < 0 & Percent_Dep_Dchange <= -50, "Both_Responder", 
      ifelse(CUXOS_pre > 10 & Percent_Anx_change  <= -50, "Anx Responder",
      ifelse(CUDOS_pre > 10 & Percent_Dep_Dchange <= -50, "Dep Responder",
      ifelse(CUDOS_pre > 10 & Percent_Dep_Dchange > 0 & CUXOS_pre > 10 & Percent_Anx_change > 0, "Both Worse",
      ifelse(CUXOS_pre > 10 & Percent_Anx_change > 0, "Anx Worse",
      ifelse(CUDOS_pre > 10 & Percent_Dep_Dchange > 0, "Dep Worse",
      ifelse(CUXOS_pre > 10 & CUDOS_pre > 10 & Percent_Anx_change < 0 & Percent_Anx_change > -50 & Percent_Dep_Dchange < 0 & Percent_Dep_Dchange > -50, "Both Unresponder",
      ifelse(CUDOS_pre > 10 & Percent_Dep_Dchange < 0 & Percent_Dep_Dchange > -50, "Dep Unresponders", 
      ifelse(CUXOS_pre > 10 & Percent_Anx_change < 0 & Percent_Anx_change > -50, "Anx Unresponders", "Low Baseline"
      )))))))))))

 #CUXOS_post == !(CUXOS_post %in% c(seq(1,9,1)))

ggplot(Mothership_post, aes(x = Treatment_Responder)) +
  geom_bar() +
  coord_flip() +
  scale_x_discrete(limits =c("Low Baseline", "Both Worse", "Dep Worse", "Anx Worse","Both Unresponder","Dep Unresponders", "Anx Unresponders","Both_Responder", "Anx Responder","Dep Responder"))+
  labs(
    title = "Treatment response of Anxiety and Depression",
    subtitle = "Response = 50% reduciton in scores if BL score > 10")

ggplot(Mothership_post, aes(x = Anx_Responder)) +
  geom_bar() +
  coord_flip() +
    labs(
    title = "Treatment response of Anxiety",
    subtitle = "Response = 50% reduciton in scores if BL score > 10")

ggplot(Mothership_post, aes(x = Dep_Responder)) +
  geom_bar() +
  coord_flip() +
    labs(
    title = "Treatment response of Depression",
    subtitle = "Response = 50% reduciton in scores if BL score > 10")
```

What Doug Wants

# Results
### The overall breakdown of patients’ demographics and diagnoses. 
Table – Demographics
Table – Diagnoses
```{r}
#Demographics Table
Demo_tab_df <- Mothership_Diag_treat |>
  filter(!is.na(Education_1),
         !is.na(Race_1),
         !is.na(Gender_1),
         !is.na(Disorder_Type),
         !is.na(Relationship_1)
        )

@@

#Disorder Table - duratin
Dis_tab <- data.frame(table1::table1(~Disorder_Type | Duration, data = Mothership_Diag_treat))
colnames(Dis_tab) <- c("Primary Diagnosis","1-5 Days", "6-10 Days", "11-15 Days","16+ Days", "Total Sample")
Dis_tab

#Disorder Tab by 10 days
Dis_tab_10 <- data.frame(table1::table1(~Disorder_Type | Duration_10, data = Mothership_Diag_treat))
colnames(Dis_tab_10) <- c("Primary Diagnosis","1-10 Days", "10+ Days", "Total Sample")
Dis_tab_10

@@

Dumbell Plot by Disorder
```{r}
AnxDep_PrePost <- data.frame(cbind(Mothership_post$ID1,
                                  Mothership_post$Disorder_Type,
                                  Mothership_post$pre_anx,
                                  Mothership_post$post_anx,
                                  Mothership_post$pre_dep,
                                  Mothership_post$post_dep)) 
  # filter(!is.na(Mothership_post$Disorder_Type))
colnames(AnxDep_PrePost) = c("ID1","Disorder_Type", "CUDOS_pre","CUDOS_post","CUXOS_pre","CUXOS_post")

@@

ggplot(data=Pre_ANX,
       aes(x=Disorder_Type,y=Score,
           group=Disorder_Type,color=Disorder_Type))+
  geom_segment(aes(x=Disorder_Type, xend=Post_ANX$Disorder_Type, y=Score, yend=Post_ANX$Score),color = "#ad3e4f",
              size = 4, #Note that I sized the segment to fit the points
              alpha = .5) +
  geom_point( aes(x=Disorder_Type, y=Score), color= "#F90000", size=3.5) +
  geom_point( aes(x=Post_ANX$Disorder_Type, y=Post_ANX$Score), color= "#0CC541", size=3.5) +
  labs(title = "Mean Pre and Post Anxiety Scores By Disorder Type",
       subtitle = "Self Report anxiety was assessed using the CUXOS",
       caption = "Symptom severity: 0-10 (remission), 11-20 (minimal), 21-30 (mild), 31-40 (moderate), 41+ (severe)")+
  scale_y_reverse(limits = c(45,15)) +
  coord_flip() +
  theme_classic()+
  facet_wrap(~RESPONDER_FIGS,labeller = labeller(RESPONDER_FIGS =
      c("1" = "Non-Responders", 
        "2" = "Responders")
  ))
  theme(#legend.position = "none",
         plot.background = element_rect(
      fill = "white",
      colour = "white"))

@@

### Education Status
```{r}
ggplot(data = subset(Mothership, !is.na(Education_1)),mapping = aes(x = Education_1))+
  geom_bar(color = "black",fill="darkred")+
  ggtitle("Frequency of Education Level") +
  theme(axis.text.x = element_text(angle = 45,hjust = 1))+
  xlab("Education Level")+
  theme(panel.grid.major.x = element_line(color = "grey",linewidth = 0.5,linetype = 2))+
  theme(panel.background=NULL)+
  scale_y_continuous(name = "Frequency",limits=c(0,3000))+
  coord_flip()
```

### Race
```{r}
ggplot(data = subset(Mothership, !is.na(Race_1)),mapping = aes(x = Race_1))+
  geom_bar(color = "black",fill="darkblue")+
  ggtitle("Frequency of Race/Ethnicity") +
  theme(axis.text.x = element_text(angle = 45,hjust = 1))+
  xlab("Race")+
  theme(panel.grid.major.y = element_line(color = "grey",size = 0.5,linetype = 2))+
  theme(panel.background=NULL)+
  scale_y_continuous(name = "Frequency",limits=c(0,6500)) +
  coord_flip()
```

### Gender
```{r}
ggplot(data = subset(Mothership, !is.na(Gender_1)),mapping = aes(x = Gender_1))+
  geom_bar(color = "black",fill="darkorange")+
  ggtitle("Frequency of Gender") +
  theme(axis.text.x = element_text(angle = 45,hjust = 1))+
  xlab("Gender")+
  theme(panel.grid.major.y = element_line(color = "grey",size = 0.5,linetype = 2))+
  theme(panel.background=NULL)+
  coord_flip()+
  scale_y_continuous(name = "Frequency",limits=c(0,6500))
```

# Pie Chart For Education Status 
We wanted to learn how to make a pie chart in R so here is one!
```{r}
#Create Table and Data Frame
Education<-table(Mothership$Education_1)
Education_df<-as.data.frame(Education)
Education_df

#Rename Columns
colnames(Education_df)[1]="Category"
colnames(Education_df)[2]="Frequency"

Education_df$Category=recode(Education_df$Category,
                             "0"="<Grade 6", 
                             "1"="Grades 7-12",
                             "2"="HS Diploma", 
                             "3"="GED",
                             "4"="Some College",
                             "5"="Associates Degree",
                             "6"="Bachelors Degree",
                             "7"="Some Grad School",
                             "8"="Grad Degree")

ggplot(data = Education_df, mapping = aes(x="", y=Frequency, fill=Category))+
  geom_bar(stat="Identity",width=1,color="white")+
  ggtitle("Education Level of Patients") +
  scale_fill_discrete(name = "Education") +
  coord_polar("y",start=0)+
  theme_void()
```

@@

ggplot(data = subset(Mothership, !is.na(IPT_track_1)),mapping = aes(x = IPT_track_1))+
  geom_bar(color = "black",fill="skyblue")+
  ggtitle("Frequency of Treatment Type") +
  theme(axis.text.x = element_text(angle = 45,hjust = 1))+
  xlab("Treatment Type")+
  theme(panel.grid.major.x= element_line(color = "grey",size = 0.5,linetype = 2))+
  theme(panel.background=NULL)+
  scale_y_continuous(name = "Frequency",limits=c(0,4200))+
  coord_flip()
```

@@

ggplot(data = subset(Mothership, !is.na(TxYear)),mapping = aes(x = TxYear))+
  geom_bar(color = "black",fill="#9350C7")+
  ggtitle("Frequency of Patients per Year") +
  theme(axis.text.x = element_text(angle = 45,hjust = 1))+
  xlab("Treatment Year")+
  theme(panel.grid.major.x = element_line(color = "grey",size = 0.5,linetype = 2))+
  theme(panel.background=NULL)+
  scale_y_continuous(name = "Frequency",limits=c(0,1500)) +
  coord_flip()
```

### Duration of Treatment
```{r}
### Duration of Treatment ###
ggplot(data = subset(Mothership, !is.na(Duration)),mapping = aes(x = Duration))+
  geom_bar(color = "black",fill="lightgreen")+
  ggtitle("Frequency of Patients per Duration of Treatment") +
  theme(axis.text.x = element_text(angle = 45,hjust = 1))+
  xlab("Treatment Duration")+
  theme(panel.grid.major.x = element_line(color = "grey",size = 0.5,linetype = 2))+
  theme(panel.background=NULL)+
  scale_y_continuous(name = "Frequency",limits=c(0,3000))+
  coord_flip()

>>>>

# Prep data for analysis

Read in the dataset. 
```{r}
Mothership <- read_sav("~/Desktop/Coding/data/PHPoutcome_clean.sav")
head(df)
```

@@

####  Export as CSV
write.csv(Mothership,"~/Desktop/Coding/data/Mothership_paper")

####. Disorder_variables

@@

# df with and without depression
No_depressy <- Mothership_Diag %>%
  filter(Disorder_Type != "Mood")

############.          Extract pre/post scores.   ######################

#1. load DF
    Mothership_post <- Mothership_Diag_treat

@@

    # Anxiety
    Pre_ANX <- NA
    PA_df <- NA
    for(i in 1:nrow(CUXOS_Score_pre)){
    PA_df <- unname(unlist(CUXOS_Score_pre[i,]))
    PA_df <- PA_df[!is.na(PA_df)]
    PA_df <- head(PA_df, n=1)
    Pre_ANX <- rbind(Pre_ANX,PA_df)
    }
    Pre_anx <- Pre_ANX[-1]

@@

              #deprssion values Symptom severity: 0-10 (remission), 11-20 (minimal), 21-30 (mild), 31-45 (moderate), 46+ (severe)"
        BL_Dep_level = as.factor(ifelse(BL_CUDOS > 10 & BL_CUDOS <= 20, "Minimal",
                                 ifelse(BL_CUDOS > 20 & BL_CUDOS <= 30, "Mild",
                                 ifelse(BL_CUDOS > 10 & BL_CUDOS <= 45, "Moderate",
                                 ifelse(BL_CUDOS > 45, "Severe",
                                 ifelse(is.na(BL_CUDOS), NA, "Remission"
                                )))))),
        BL_Anx_level = as.factor(ifelse(BL_CUXOS > 10 & BL_CUXOS <= 20, "Minimal",
                                 ifelse(BL_CUXOS > 20 & BL_CUXOS <= 30, "Mild",
                                 ifelse(BL_CUXOS > 10 & BL_CUXOS <= 45, "Moderate",
                                 ifelse(BL_CUXOS > 45, "Severe",
                                 ifelse(is.na(BL_CUXOS), NA, "Remission"
                                )))))),
        Post_Dep_level = as.factor(ifelse(CUDOS_post > 10 & CUDOS_post <= 20, "Minimal",
                                 ifelse(CUDOS_post > 20 & CUDOS_post <= 30, "Mild",
                                 ifelse(CUDOS_post > 10 & CUDOS_post <= 45, "Moderate",
                                 ifelse(CUDOS_post > 45, "Severe",
                                 ifelse(is.na(CUDOS_post), NA, "Remission"
                                )))))),
        Post_Anx_level = as.factor(ifelse(CUXOS_post > 10 & CUXOS_post <= 20, "Minimal",
                                 ifelse(CUXOS_post > 20 & CUXOS_post <= 30, "Mild",
                                 ifelse(CUXOS_post > 10 & CUXOS_post <= 45, "Moderate",
                                 ifelse(CUXOS_post > 45, "Severe",
                                 ifelse(is.na(CUXOS_post), NA, "Remission"
                                )))))))

############                       Responder                   ############ 
#devtools::install_github("AWKruijt/JT-RCI")

library(JTRCI)
library(ClinicalSig)

#devtools::install_github("zieglema/ClinicalSig")

@@

RCI_DF

###############          Adding RCI to dataset       ####################

Mothership_post <- Mothership_post |>
  #1. Filter out scores for people not in the program / don't have dataa
  filter(!is.na(Days_complete_1)) |>
    #Having people in the program for more than 40 days means that their scores may be a lot higher, they should be filtered out as result. 
  filter(!is.na(CUXOS_pre),
         !is.na(CUXOS_post),
         CUXOS_pre > 0,
         CUXOS_post >= 0,
         !is.na(CUDOS_pre),
         !is.na(CUDOS_post),
         CUDOS_pre > 0,
         CUDOS_post> 0
         ) |>
  mutate(
    Delta_Anx_DC =  CUXOS_post - CUXOS_pre,
    Delta_Dep_DC = CUDOS_post - CUDOS_pre,
    Percent_Anx_change = (Delta_Anx_DC/CUXOS_pre)*100,
    Percent_Dep_Dchange = (Delta_Dep_DC/CUDOS_pre)*100,
    #Days_complete_W = ifelse(Days_complete_1 > 40, 40, Days_complete_1),
    Anx_Responder = as.factor(
      ifelse(CUXOS_pre < 20 & Percent_Anx_change  <= -50, "Responder",
      ifelse(CUXOS_pre < 20 & Percent_Anx_change  > -50,  "Unresponders", NA)   
      )),
    Dep_Responder = as.factor(
      ifelse(CUDOS_pre < 20 & Percent_Dep_Dchange <= -50, "Responder",
      ifelse(CUDOS_pre < 20 & Percent_Dep_Dchange > -50,   "Unresponders", NA) 
      )),
    Treatment_Responder = as.factor(
      ifelse(CUXOS_pre > 10 & CUXOS_pre > 10 & Percent_Anx_change  <= -50 & Percent_Anx_change < 0 & Percent_Dep_Dchange < 0 & Percent_Dep_Dchange <= -50, "Both_Responder", 
      ifelse(CUXOS_pre > 10 & Percent_Anx_change  <= -50, "Anx Responder",
      ifelse(CUDOS_pre > 10 & Percent_Dep_Dchange <= -50, "Dep Responder",
      ifelse(CUDOS_pre > 10 & Percent_Dep_Dchange > 0 & CUXOS_pre > 10 & Percent_Anx_change > 0, "Both Worse",
      ifelse(CUXOS_pre > 10 & Percent_Anx_change > 0, "Anx Worse",
      ifelse(CUDOS_pre > 10 & Percent_Dep_Dchange > 0, "Dep Worse",
      ifelse(CUXOS_pre > 10 & CUDOS_pre > 10 & Percent_Anx_change < 0 & Percent_Anx_change > -50 & Percent_Dep_Dchange < 0 & Percent_Dep_Dchange > -50, "Both Unresponder",
      ifelse(CUDOS_pre > 10 & Percent_Dep_Dchange < 0 & Percent_Dep_Dchange > -50, "Dep Unresponders", 
      ifelse(CUXOS_pre > 10 & Percent_Anx_change < 0 & Percent_Anx_change > -50, "Anx Unresponders", "Low Baseline"
      )))))))))))

RCI_DF

Mothership_post <- left_join(Mothership_post,RCI_DF, by = join_by(ID1 == ID1)) |>
  mutate(
    Depression_Responder = ifelse(!is.na(class_RCI_dep), class_RCI_dep, NA),
      Depression_Responder = as.factor(recode(Depression_Responder,
         "1" = "2",
         "2" = "2",
         "3" = "1"
      )),
    Depression_Responder = as.factor(ifelse(!is.na(Depression_Responder), Depression_Responder, Dep_Responder)),
         Depression_Responder = as.factor(recode(Depression_Responder,
          "2" = "Non-Responder",
          "1" = "Responder"
      )),
    Anxiety_Responder = ifelse(!is.na(class_RCI_anx), class_RCI_anx, NA),
      Anxiety_Responder = as.factor(recode(Anxiety_Responder,
         "1" = "2",
         "2" = "2",
         "3" = "1"
      )),
    Anxiety_Responder = as.factor(ifelse(!is.na(Anxiety_Responder), Anxiety_Responder, Anx_Responder)),
         Anxiety_Responder = as.factor(recode(Anxiety_Responder,
          "2" = "Non-Responder",
          "1" = "Responder"
      )),
    RESPONDER_FIGS = as.factor(
        ifelse(Anxiety_Responder == "Responder" | Depression_Responder == "Responder", "Responder",
        ifelse(Anxiety_Responder == "Non-Responder" & Depression_Responder == "Non-Responder", "Non-Responder", NA)
        )))

#############            AnxDep_PrePost                 ##################

#7. create new DF with Varaibles we want

@@

What I Want

# Results
### The overall breakdown of patients’ demographics and diagnoses. 
Table – Demographics
Table – Diagnoses
```{r}
#Demographics Table
Demo_tab_df <- Mothership_post |>
  #Mothership_Diag_treat |>
  filter(!is.na(Education_1),
         !is.na(Race_1),
         !is.na(Gender_1),
         !is.na(Disorder_Type),
         !is.na(Relationship_1)
        )

@@

#Disorder Table - duratin
Dis_tab <- data.frame(table1::table1(~Disorder_Type | Duration, data = Mothership_post))
                                       #Mothership_Diag_treat))
colnames(Dis_tab) <- c("Primary Diagnosis","1-5 Days", "6-10 Days", "11-15 Days","16+ Days", "Total Sample")
Dis_tab

#Disorder Tab by 10 days
Dis_tab_10 <- data.frame(table1::table1(~Disorder_Type | Duration_10, data = Mothership_post))
                                      #Mothership_Diag_treat))
colnames(Dis_tab_10) <- c("Primary Diagnosis","1-10 Days", "10+ Days", "Total Sample")
Dis_tab_10

##### Add other demographic information here

@@

Dumbell Plot by Disorder
```{r}
AnxDep_PrePost <- data.frame(cbind(Mothership_post$ID1,
                                  Mothership_post$Disorder_Type,
                                  Mothership_post$pre_anx,
                                  Mothership_post$post_anx,
                                  Mothership_post$pre_dep,
                                  Mothership_post$post_dep,
                                  Mothership_post$RESPONDER_FIGS)) 
  # filter(!is.na(Mothership_post$Disorder_Type))
colnames(AnxDep_PrePost) = c("ID1","Disorder_Type", "CUDOS_pre","CUDOS_post","CUXOS_pre","CUXOS_post","RESPONDER_FIGS)")

@@

ggplot(data=AnxDep_PrePost,
       aes(x=Disorder_Type,y=Score,
           group=Disorder_Type,color=Disorder_Type))+
  geom_segment(aes(x=Disorder_Type, xend=Post_ANX$Disorder_Type, y=Score, yend=Post_ANX$Score),color = "#ad3e4f",
              size = 4, #Note that I sized the segment to fit the points
              alpha = .5) +
  geom_point( aes(x=Disorder_Type, y=Score), color= "#F90000", size=3.5) +
  geom_point( aes(x=Post_ANX$Disorder_Type, y=Post_ANX$Score), color= "#0CC541", size=3.5) +
  labs(title = "Mean Pre and Post Anxiety Scores By Disorder Type",
       subtitle = "Self Report anxiety was assessed using the CUXOS",
       caption = "Symptom severity: 0-10 (remission), 11-20 (minimal), 21-30 (mild), 31-40 (moderate), 41+ (severe)")+
  scale_y_reverse(limits = c(45,15)) +
  coord_flip() +
  theme_classic()+
  facet_wrap(~RESPONDER_FIGS,labeller = labeller(RESPONDER_FIGS =
      c("1" = "Non-Responders", 
        "2" = "Responders")
  ))
  theme(#legend.position = "none",
         plot.background = element_rect(
      fill = "white",
      colour = "white"))

@@

### Education Status
```{r}
ggplot(data = subset(Mothership_post, !is.na(Education_1)),mapping = aes(x = Education_1))+
  geom_bar(color = "black",fill="darkred")+
  ggtitle("Frequency of Education Level") +
  theme(axis.text.x = element_text(angle = 45,hjust = 1))+
  xlab("Education Level")+
  theme(panel.grid.major.x = element_line(color = "grey",linewidth = 0.5,linetype = 2))+
  theme(panel.background=NULL)+
  scale_y_continuous(name = "Frequency",limits=c(0,3000))+
  coord_flip()
```

### Race
```{r}
ggplot(data = subset(Mothership_post, !is.na(Race_1)),mapping = aes(x = Race_1))+
  geom_bar(color = "black",fill="darkblue")+
  ggtitle("Frequency of Race/Ethnicity") +
  theme(axis.text.x = element_text(angle = 45,hjust = 1))+
  xlab("Race")+
  theme(panel.grid.major.y = element_line(color = "grey",size = 0.5,linetype = 2))+
  theme(panel.background=NULL)+
  scale_y_continuous(name = "Frequency",limits=c(0,6500)) +
  coord_flip()
```

### Gender
```{r}
ggplot(data = subset(Mothership_post, !is.na(Gender_1)),mapping = aes(x = Gender_1))+
  geom_bar(color = "black",fill="darkorange")+
  ggtitle("Frequency of Gender") +
  theme(axis.text.x = element_text(angle = 45,hjust = 1))+
  xlab("Gender")+
  theme(panel.grid.major.y = element_line(color = "grey",size = 0.5,linetype = 2))+
  theme(panel.background=NULL)+
  coord_flip()+
  scale_y_continuous(name = "Frequency",limits=c(0,6500))
```

@@

ggplot(data = subset(Mothership_post, !is.na(IPT_track_1)),mapping = aes(x = IPT_track_1))+
  geom_bar(color = "black",fill="skyblue")+
  ggtitle("Frequency of Treatment Type") +
  theme(axis.text.x = element_text(angle = 45,hjust = 1))+
  xlab("Treatment Type")+
  theme(panel.grid.major.x= element_line(color = "grey",size = 0.5,linetype = 2))+
  theme(panel.background=NULL)+
  scale_y_continuous(name = "Frequency",limits=c(0,4200))+
  coord_flip()
```

@@

ggplot(data = subset(Mothership_post, !is.na(TxYear)),mapping = aes(x = TxYear))+
  geom_bar(color = "black",fill="#9350C7")+
  ggtitle("Frequency of Patients per Year") +
  theme(axis.text.x = element_text(angle = 45,hjust = 1))+
  xlab("Treatment Year")+
  theme(panel.grid.major.x = element_line(color = "grey",size = 0.5,linetype = 2))+
  theme(panel.background=NULL)+
  scale_y_continuous(name = "Frequency",limits=c(0,1500)) +
  coord_flip()
```

### Duration of Treatment
```{r}
### Duration of Treatment ###
ggplot(data = subset(Mothership_post, !is.na(Duration)),mapping = aes(x = Duration))+
  geom_bar(color = "black",fill="lightgreen")+
  ggtitle("Frequency of Patients per Duration of Treatment") +
  theme(axis.text.x = element_text(angle = 45,hjust = 1))+
  xlab("Treatment Duration")+
  theme(panel.grid.major.x = element_line(color = "grey",size = 0.5,linetype = 2))+
  theme(panel.background=NULL)+
  scale_y_continuous(name = "Frequency",limits=c(0,3000))+
  coord_flip()
